---
title: "ANA 515 Week 5 Visualizations Activity"
author: "Gyu Hyun Byun"
date: "2022-09-25"
output:
  word_document: default
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyselect)
library(tinytex)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```
##
## Reading the data into R and Cleaning the Data
##
The data is read into R, sorted by the variable, total_litres_of_pure_alcohol in reverse order.
Then, the data is filtered to focus on the top 10 countries with the highest pure alcohol consumption.

```{r echo = TRUE}
drinks <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/50ec9ccfe3aa20f328bfd5e5da584fa5e15efee6/alcohol-consumption/drinks.csv")
drinks <- drinks[order(-drinks$total_litres_of_pure_alcohol),]
drinks <- drinks[1:10,]
drinks$country <- factor(drinks$country, levels = drinks$country[order(-drinks$total_litres_of_pure_alcohol)])
```
##
## Visualization #1: Bar Plot
##
The graph shows the top 10 alcohol consuming countries by their total liters of pure alcohol consumption per person per year.

```{r, echo = TRUE}
barplot(main = "Top 10 Alcohol Consuming Countries", height = drinks$total_litres_of_pure_alcohol, names = drinks$country, las=2, border="black", col="white")
```

##
## Visualization #2: GGPlot Geom Bar Graph
##
The graph shows the top 10 alcohol consuming countries with their wine consumption in RED, beer consumption in YELLOW, and spirit consumption in BLUE. 

```{r, echo = TRUE}
ggplot(drinks) + geom_bar(aes(x = country, y = beer_servings), stat = "identity", color="yellow", fill=NA, size=2) + geom_bar(aes(x = country, y = spirit_servings), stat = "identity", color="blue", fill=NA, size=2) + geom_bar(aes(x = country, y = wine_servings), stat = "identity", color="red", fill=NA, size=2) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(title="Top 10 Alcohol Consuming Countries by Drink Type", x = "Country", y = "Consumption")
```
